Causal_Analysis_Paper

### 2022-05-30 PaperAnalysis.Rmd
Some work on the indicators, other restrictions and clinical aspects of abortion datasets

@@

## Original paper
- Latt, S.M., Milner, A. & Kavanagh, A.(2019) Abortion laws reform may reduce maternal mortality: an ecological study in 162 countries. BMC Women's Health 19, 1. https://doi.org/10.1186/s12905-018-0705-y

## Origital paper datasets
-   UN (2013). Population division. World Abortion policies 2013.  [Accessible here](https://www.un.org/en/development/desa/population/publications/policy/world-abortion-policies-2013.asp)

## Updated datasets
- WHO. (2022). Global Abortion Policies Worldwide. [Accessible here](https://abortion-policies.srhr.org/)

@@

## Other Resources

>>>>

In "Abortion laws reform may reduce maternal mortality: an ecological study in 162 countries," Latt, Milner and Kavanagh present the results of a study that aims to assess whether maternal mortality is affected by the flexibility of abortion laws.

@@

## Original Paper
- Latt, S.M., Milner, A. & Kavanagh, A.(2019) Abortion laws reform may reduce maternal mortality: an ecological study in 162 countries. BMC Women's Health 19, 1. https://doi.org/10.1186/s12905-018-0705-y

## Datasets
### Origital paper datasets
-   UN (2013). Population division. World Abortion policies 2013.  [Accessible here](https://www.un.org/en/development/desa/population/publications/policy/world-abortion-policies-2013.asp)

### Updated datasets
- WHO. (2022). Global Abortion Policies Worldwide. [Accessible here](https://abortion-policies.srhr.org/)

@@

### Other Data sets

-	OSF. (2020). Global abortion Incidence (https://osf.io/6t4eh/)

- - WHO. (2022). Global Abortion Laws. [Accessible here](https://abortion-policies.srhr.org/)

-	Health system. (https://apps.who.int/nha/database), hospital beds (https://data.worldbank.org/indicator/SH.MED.BEDS.ZS)
-	Economic: GPD, human capital (education, as in Jensen paper), poverty (https://data.worldbank.org/indicator/SI.POV.NAHC), GINI (https://data.worldbank.org/indicator/SI.POV.GINI)

- life expectancy at birth (https://data.worldbank.org/indicator/SP.DYN.LE00.IN)
